You can be Shakespeare! \\ A Case Study in Paraphrase Targeting Writing Styles

### 2012-08-29 paper/paper.tex
more proofreading...

Although two utterances might be semantically equivalent, they can still be stylistically quite different.  For example, the same information
is likely to be conveyed using very different lexical and grammatical patterns in advertising materials v.s. technical manuals, or in Shakespearean plays v.s. Hollywood movies.

Systems capable of paraphrasing text targeting a specific writing style could be useful for a variety of applications.  For example, they could:
\begin{enumerate}
  \item Help authors of technical documents to adhere to appropriate stylistic guidelines.  
  \item Enable average people to better understand information in legal documents by translating ``legalese'' into ordinary English.  
  \item Benefit educational applications:
    \begin{enumerate}
    \item Students studying a specific style of writing may benefit from access to \emph{modern English} versions of works by authors they are studying.
    \item Automatic paraphrases could help students to experiment with writing in the style of the authors whose works they are reading.
    \end{enumerate}
\end{enumerate}

@@

We evaluate these models both through human judgments and standard evaluation metrics from the Machine Translation and Paraphrase literature, however no previous work has investigated the ability of automatic
evaluation metrics to capture the notion of writing style.  
We show that previously proposed metrics do not provide the complete picture of a system's performance when the task is to generate paraphrases
targeting a specific style of writing.  We propose two new metrics for evaluating paraphrases targeting a specific style, and measure correlation with human judgments showing promising
preliminary results.

@@

We compare 3 different stylistic paraphrase systems targeting Shakespearean English.  One which leverages parallel corpora of modern translations, another which makes use
of dictionaries of stylistically representative expressions, and another which utilizes out-of-domain monolingual parallel data.

@@

\subsubsection{Discussion}
Two main trends emerge from Figure \ref{bleupinc}.  First, notice that all of the systems which are trained using parallel text achieve higher BLEU scores than the baseline
of not making any changes to the modern translations.  While the dictionary baseline achieves a competitive PINC score, indicating it is making a significant number of changes to the 
input, it's BLEU is lower than the \emph{no changes} baseline.  Secondly, it seems apparent that the systems whose parameters are tuned using Minimum Error Rate Training \cite{MERT}
tend to be more conservative, making fewer changes to the input and thus achieving lower PINC scores, however also not seeing any BLEU improvements on the test data.  Finally
we note that using the larger language model seems to yield a slight improvement in BLEU score.

@@

\begin{table}
  \begin{center}
    \begin{tabular}{|l|p{3in}|}
      \hline
      System & Description \\
      \hline
      \hline
      16and7plays\_36LM & Phrase table learned from all 16 Sparknotes plays (other than R\&J) and language model built from all 36 of Shakespeare's plays, excluding R\&J.
      Uses default Moses parameters. \\
      \hline
      16and7plays\_36LM\_MERT & Same as 16and7plays\_36LM except parameters are tuned using Minimum Error Rate Training \cite{MERT} instead of using the default Moses parameters.\\
      \hline
      16and7plays\_16LM & Phrase table is built from both Sparknotes and Enotes data, and Language model is built from the 16 with modern translations\\
      \hline
      16and7plays\_16LM\_MERT & Same as 16and7plays\_16LM except parameters are tuned using MERT. \\
      \hline
      16plays\_36LM & Only Sparknotes modern translations are used.  All 36 plays are used to train Shakespearean language model.\\
      \hline
      16plays\_36LM\_MERT & Same as 16plays\_36LM except parameters are tuned using MERT. \\
      \hline
      video\_corpus\_baseline & Paraphrase system combining out of domain parallel text \cite{chen11} with an in-domain language model.  Described
      in detail in section \ref{video_baseline}. \\
      \hline
      modern (no change) & No changes are made to the input, modern translations are left unchanged. \\
      \hline
      Dictionary & Dictionary baseline described in section \ref{dictionary_baseline}\\
      \hline
    \end{tabular}
  \end{center}
  \caption{Descriptions of various systems for Shakespearean Paraphrase.  {\em Romeo and Juliet} is held out for testing.}
  \label{systems}
\end{table}

@@

While BLEU is typically used to measure semantic adequacy, it seems reasonable to assume that it may also depend on style, since utterances
are more likely to contain overlapping ngrams if they are both semantically and stylistically similar.  What BLEU doesn't tell us, however
is what portion of it's improvements are due to stylistic similarity or semantic equivalence.  For this reason, we were motivated perform
an evaluation based on human judgments of semantic adequacy, lexical dissimilarity and stylistic similarity.

For this purpose, we randomly sampled 100 lines from {\em Romeo and Juliet}, then two of the authors annotated each sentence and it's Shakespearean
translation with semantic adequacy, lexical dissimilarity, stylistic similarity, and overall quality.
The aggregate results of the human evaluation are displayed in figure \ref{human_judgements}.  Agreement between annotators
measured using Pearson's $\rho$ is displayed in table \ref{annotator_agreement}.

@@

These results are roughly in line with the automatic evaluation metrics presented in figure \ref{bleupinc}, however we also see several important
trends which are not apparent from the automatic evaluation metrics.
Although the video baseline achieves the highest semantic adequacy in the human evaluation, it's BLEU score
is significantly lower than 16plays\_36LM on the Sparknotes data.\footnote{
Note that the BLEU score of 16plays\_36LM is significantly lower when evaluated on the Enotes data.  This makes sense, because the 
16 plays come from Sparknotes. This system is not trained on the 7 Enotes plays which, whose modern translations tend
to be slightly different in style.}
It would appear that in this case BLEU is conflating semantic adequacy with writing style.  Although the paraphrases produced 
by the video baseline have high semantic adequacy, their style tends to differ substantially from the reference translations resulting
in fewer ngram matches, and thus a lower BLEU score.

@@

\begin{figure}
  \includegraphics[width=5in]{figures/shakespeare_to_modern.pdf}
  \caption{Automatic evaluation of paraphrasing Shakespeare's plays into modern english comparing a system based on parallel text (16plays\_16LM), 
  a Dictionary baseline, and a system trained on out of domain parallel monolingual text.  Note that the video corpus baseline achieves low overal
  PINC score, as few phrases in the input match phrases found in it's phrase table, resulting in a small number of changes to the input.}
  \label{shakespeare_to_modern_automatic}
\end{figure}

>>>>

Although two utterances may be semantically equivalent, they can still be stylistically quite different.  For example, the same information
is likely to be conveyed using very different lexical and grammatical patterns in advertising materials v.s. technical manuals, or in Shakespearean plays v.s. Hollywood movies.

Systems capable of paraphrasing text targeting a specific writing style could be useful for a variety of applications.  For example, they could:
\begin{enumerate}
  \item Help authors of technical documents to adhere to appropriate stylistic guidelines.  
  \item Enable average people to better understand information in legal documents by translating ``legalese'' into ordinary English.  
  \item Benefit educational applications:
    \begin{enumerate}
    \item Students studying a specific literary style may benefit from access to \emph{modern English} versions of works by authors they are studying.
    \item Automatic paraphrases could help students to experiment with writing in the style of the authors they are studying.
    \end{enumerate}
\end{enumerate}

@@

We evaluate these models both through human judgments and standard evaluation metrics from the Machine Translation and Paraphrase literature, however no previous work has investigated the ability of automatic
evaluation metrics to capture the notion of writing style.  
We show that previously proposed metrics do not provide the complete picture of a system's performance when the task is to generate paraphrases
targeting a specific style of writing.  We therefore propose two new metrics for evaluating paraphrases targeting a specific style, and measure correlation with human judgments showing promising
preliminary results.

@@

We compare 3 different stylistic paraphrase systems targeting Shakespearean English which vary in the resources they assume access to.
One which leverages parallel corpora of modern translations, another which makes use
of dictionaries of stylistically representative expressions, and another which utilizes out-of-domain monolingual parallel data.

@@

\subsubsection{Discussion}
Two main trends emerge from Figure \ref{bleupinc}.  First, notice that all of the systems which are trained using parallel text achieve higher BLEU scores than the baseline
of not making any changes to the modern translations.  While the dictionary baseline achieves a competitive PINC score, indicating it is making a significant number of changes to the 
input, its BLEU is lower than the \emph{no changes} baseline.  Secondly, it seems apparent that the systems whose parameters are tuned using Minimum Error Rate Training \cite{MERT}
tend to be more conservative, making fewer changes to the input and thus achieving lower PINC scores, however also not seeing any BLEU improvements on the test data.  Finally
we note that using the larger language model seems to yield a slight improvement in BLEU score.

@@

\begin{table}
  \begin{center}
    \begin{tabular}{|l|p{3in}|}
      \hline
      System & Description \\
      \hline
      \hline
      16and7plays\_36LM & Phrase table extracted from all 16 Sparknotes plays (other than R\&J) and language model built from all 36 of Shakespeare's plays, again excluding R\&J.
      Uses default Moses parameters. \\
      \hline
      16and7plays\_36LM\_MERT & Same as 16and7plays\_36LM except parameters are tuned using Minimum Error Rate Training \cite{MERT}. \\
      \hline
      16and7plays\_16LM & Phrase table is built from both Sparknotes and Enotes data, and Language model is built from the 16 plays with modern translations\\
      \hline
      16and7plays\_16LM\_MERT & Same as 16and7plays\_16LM except parameters are tuned using MERT. \\
      \hline
      16plays\_36LM & Only Sparknotes modern translations are used.  All 36 plays are used to train Shakespearean language model.\\
      \hline
      16plays\_36LM\_MERT & Same as 16plays\_36LM except parameters are tuned using MERT. \\
      \hline
      video\_corpus\_baseline & Paraphrase system combining out of domain parallel text \cite{chen11} with an in-domain language model.  Described
      in detail in section \ref{video_baseline}. \\
      \hline
      modern (no change) & No changes are made to the input, modern translations are left unchanged. \\
      \hline
      Dictionary & Dictionary baseline described in section \ref{dictionary_baseline}\\
      \hline
    \end{tabular}
  \end{center}
  \caption{Descriptions of various systems for Shakespearean Paraphrase.  {\em Romeo and Juliet} is held out for testing.}
  \label{systems}
\end{table}

@@

While BLEU is typically used to measure semantic adequacy, it seems reasonable to assume that it may also depend on style, since utterances
are more likely to contain overlapping ngrams if they are both semantically and stylistically similar.  What BLEU doesn't tell us, however
is what portion of its improvements are due to stylistic similarity or semantic equivalence.  For this reason, we were motivated perform
an evaluation based on human judgments of semantic adequacy, lexical dissimilarity and stylistic similarity.

For this purpose, we randomly sampled 100 lines from {\em Romeo and Juliet}, then two of the authors annotated each sentence and its Shakespearean
translation with semantic adequacy, lexical dissimilarity, stylistic similarity, and overall quality.
The aggregate results of the human evaluation are displayed in figure \ref{human_judgements}.  Agreement between annotators
measured using Pearson's $\rho$ is displayed in table \ref{annotator_agreement}.

@@

These results are roughly in line with the automatic evaluation metrics presented in figure \ref{bleupinc}, however we also see several important
trends which are not apparent from the automatic metrics.
Although the video baseline achieves the highest semantic adequacy in the human evaluation, its BLEU score
is significantly lower than 16plays\_36LM on the Sparknotes data.\footnote{
Note that the BLEU score of 16plays\_36LM is significantly lower when evaluated on the Enotes data.  This makes sense, because the 
16 plays come from Sparknotes. This system is not trained on the 7 Enotes plays which, whose modern translations tend
to be slightly different in style.}
It would appear that in this case BLEU is conflating semantic adequacy with writing style.  Although the paraphrases produced 
by the video baseline have high semantic adequacy, their style tends to differ substantially from the reference translations resulting
in fewer ngram matches, and thus a lower BLEU score.

@@

\begin{figure}
  \includegraphics[width=5in]{figures/shakespeare_to_modern.pdf}
  \caption{Automatic evaluation of paraphrasing Shakespeare's plays into modern english comparing a system based on parallel text (16plays\_16LM), 
  a Dictionary baseline, and a system trained on out of domain parallel monolingual text.  Note that the video corpus baseline achieves low overal
  PINC score, as few phrases in the input match phrases found in its phrase table, resulting in a small number of changes to the input.}
  \label{shakespeare_to_modern_automatic}
\end{figure}
